'Personal' Taicho repository Column(\-X) 0 1 2 3 4 5 6 7 8 9 10 11 12 13 

 0 0 10 19$|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ 

 1 1 11 20$|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ 

 2 2 12 21$|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ 

 3 $|$ 3 $|$ 13$|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ 

 Row(y) 4 $|$ 4 $|$ 14$|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ 

 5 $|$ 5 $|$ 15$|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ 

 6 6 16 $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ 

 7 7 17 $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ 

 8 8 18 $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$ \-\_\- $|$

This is a representation of the Taicho game board. The Column and Row correspond to X and Y values and the numbers on the board is each board components id. (look at docs/board.\-xls for all id's)

The Id's are used to quickly see what locations the selected character can move to. This is done by simply adding or subtracting a certain value. --Level\-One\-Legal\-Moves\-: +/-\/1, +/-\/8, +/-\/9, +/-\/10 --Level\-Two\-Legal\-Moves\-: +/-\/1, +/-\/2, +/-\/9, +/-\/18 --Level\-Three\-Legal\-Moves\-: +/-\/8, +/-\/10, +/-\/16, +/-\/20, +/-\/24, +/-\/30 --Taicho Legal Moves are calculated by finding all unoccupied squares in his castle

F\-I\-L\-E L\-I\-S\-T -\/ as of 12/23/2012 basecomponents /\-Taicho/src/basecomponents/\-Board\-Component.java --Each square on the game board corresponds to a Board\-Component(\-B\-C). It contains data pertaining to the squares state (occupied, character that occupies it, color, selected, stackable, location on game board /\-Taicho/src/basecomponents/\-Coordinate.java --simple way to find a Board\-Comonent on board. look for X, Y position or by B\-C id. /\-Taicho/src/basecomponents/\-Movable\-Object.java --class that all character objects extends. Deals with character movement. /\-Taicho/src/basecomponents/\-Object\-Move.java --another class used to simply transfer data. comprised of a starting and finishing Coordinate characters --All character objects extend the Movable\-Object class. The character object sets the Movable\-Objects player field and rank at instantiation. Most character modification should be done to the Movable\-Object.\-java file. /\-Taicho/src/characters/\-Empty\-Object.java /\-Taicho/src/characters/\-One\-Unit.java /\-Taicho/src/characters/\-Taicho.java /\-Taicho/src/characters/\-Three\-Unit.java /\-Taicho/src/characters/\-Two\-Unit.java enums /\-Taicho/src/enums/\-Level\-One\-Legal\-Moves.java /\-Taicho/src/enums/\-Level\-Three\-Legal\-Moves.java /\-Taicho/src/enums/\-Level\-Two\-Legal\-Moves.java --See Move\-Manager for these 3 enums /\-Taicho/src/enums/\-Location.java --Simple way to give each B\-C a easy to see field of where it is located on board. Possible Values\-: G\-A\-M\-E\-\_\-\-B\-O\-A\-R\-D, O\-U\-T\-\_\-\-O\-F\-\_\-\-B\-O\-U\-N\-D\-S, P\-L\-A\-Y\-E\-R\-\_\-\-O\-N\-E\-\_\-\-C\-A\-S\-T\-L\-E, P\-L\-A\-Y\-E\-R\-\_\-\-T\-W\-O\-\_\-\-C\-A\-S\-T\-L\-E /\-Taicho/src/enums/\-Player.java --Possible Values\-: P\-L\-A\-Y\-E\-R\-\_\-\-O\-N\-E, P\-L\-A\-Y\-E\-R\-\_\-\-T\-W\-O, N\-O\-N\-E /\-Taicho/src/enums/\-Ranks.java --Possible Values\-: L\-E\-V\-E\-L\-\_\-\-O\-N\-E, L\-E\-V\-E\-L\-\_\-\-T\-W\-O, L\-E\-V\-E\-L\-\_\-\-T\-H\-R\-E\-E, T\-A\-I\-C\-H\-O, N\-O\-N\-E exceptions /\-Taicho/src/exceptions/\-Board\-Component\-Not\-Found\-Exception.java --simple exception to throw when a B\-C is not found. can generally be ignored. probably want to wrap in a try/catch though... gameparts /\-Taicho/src/gameparts/\-Board.java --Interacts with the user. Contains program Action\-Listener and Mouse\-Listener. decides what the user whats to do (select character, move character, stack units, attack, etc...) --In constructor of Board there is a function parameter that when changed will change the size of the window. /\-Taicho/src/gameparts/\-Program\-Main.java --Main of program. creates board. /\-Taicho/src/gameparts/\-Taicho\-Game\-Data.java --Brains of the game. Contains board data (positions, game board, characters, players, etc...) Taicho\-Game\-Datas methods are called by Board.\-java to give it data to decide appropriate action interfaces /\-Taicho/src/interfaces/\-Move\-Manager.java --to come... ask me for now --Move\-Manager is an interface that is implemented by the enums Level\-One\-Legal\-Move.\-java, Level\-Two\-Legal\-Move.\-java, Level\-Three\-Legal\-Move.\-java. These enums contain the +/-\/ values to add to a B\-C id value to find a possible B\-C to move/attack to. Whaa?? Enums implementing interfaces, that sounds crazy? Dont worry its not too bad. Since all characters extend Movable\-Object and each Level One/\-Two/\-Three character has its own set of legal moves Level\-One\-Legal\-Move, Level\-Two\-Legal\-Move, Level\-Three\-Legal\-Move) we can simply creating a single array of Move\-Managers in a single method and and through a switch statement fill the array with the appropriate Level\-\_\-\-X\-\_\-\-Legal\-Move enums. We can then use this single array on an array list of Movable\-Object types that does not depend on the type of Movable\-Object in the array. Ask for further explanation... --Look in the get\-Possible\-Moves method of the Movable\-Object class to see how this is used utilities /\-Taicho/src/utilities/\-Board\-Dimensions.java --utility class used to easily change the size of the game window. /\-Taicho/src/utilities/\-Utils.java --utility class used to hold static methods. (contains color mixing methods at the moment) 